\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Nikant} \\
\indent Room No-138, \\
\indent Hostel no-1,  \\
\indent GNDEC,ludhiana (punjab., INDIA) - 141006\\
\indent Email-id : \textbf{Nikant20@gmail.com} \\
\indent Mobile No.: \textbf{+91 9803763824} \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{University/Board} & \textbf{Institute} & \textbf{Year} & \textbf{CGPA/\%} \\
\hline
B.tech (CSE)\,\, & Punjab Technical University & GNDEC, Ludhiana & ongoing & 73.2\% till now \\
High School & Bihar School Examination Board & VR College, Vaishali& 2013 & 78\% \\
Schooling & CBSE & KV JawaharNagar, Sitamarhi & 2010 & 9.4 CGPA\\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Data Science} and \textbf{Mobile application development}
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages} (Java SE, C++, C),\textbf{Database} (PostgreSql (Basic) ) \textbf{Script} (Python), \textbf{Tools} (Git, Android Studio, Eclipse, \LaTeX, Netbeans, Microsoft Office)
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]
\begin{itemize}
\item \textbf{\Large Sentimental Intelligence
} (Minor Project) \\
 \emph{(Guide:Prof. Sukhjit Singh
, Feb'17 - till date)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item \textbf{Objective:} Application of data science in text analysis.
.
	\item Text Analysis helps in understanding the user comments and reviews about the product.
    \item Worked on how to train a machine on various datasets.
    \item Learnt how to \textbf{process the Natural languages} in the field of Artificial Intelligence.
	\item Learnt and sucessfully implemented the various python libraries like \textbf{NLTK(Natural language Processing Toolkit), Gensim, SciPy, NumPy, Pandas} etc.

	\end{itemize}

\item \textbf{\Large TaxiFare
} (6 weeks Industrial Training) \\
 \emph{(Naresh I Technologies, Hyderabad
, Jun'16 - July'16)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item \textbf{Objective:} To provide a fair system for customers and cab drivers in generating their fare for distance travelled and time taken by the customer to reach a destination. 
	\item Worked on \textbf{Google Distance Matrix API, Google Maps API for android, Google places API} for \\android.
	\item Worked on various \textbf{Material design concepts}.
	\item Worked on \textbf{fragments} and libraries like \textbf{Firebase, Picaso, Retrofit} etc.
	\item Also have knowledge to work on JSON and server communication in android app.
	\end{itemize}
\end{itemize}

\resheading{\textbf{Ongoing Courses} }\\[\lsep]
\begin{itemize}
	\item \textbf{\small Coursera:} Machine Learning by standford university  
\end{itemize}

\resheading{\textbf{WEB \& GIT} }\\[\lsep]
\begin{itemize}
	\item \textbf{\small WEB:}  https://nikant20.wordpress.com/
	\item \textbf{\small GITHUB:} https://github.com/nikant20
\end{itemize}

\resheading{\textbf{STRENGTHS} }\\[\lsep]
\begin{itemize}
\item \noindent Positive Attitude, Self Motivated, Social Interaction, Hardworking.

\end{itemize}

\resheading{\textbf{Awards} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Google Applied Computer Science with Android Program:}\\
I have been \textbf{selected} for \textbf{Google Applied Computer Science with android program} for this year from my college.
\item \noindent \textbf{Rajya Puraskar:}\\
I was awarded with Rajya Puraskar by BHARAT SCOUT \& GUIDES for the social service. 

\end{itemize}

\end{document}

